Dynamic capabilities and competitive advantage

### 2019-10-11 article4_tommylars.rnw
testing R and P simultan

>>>>

few items less controls

      Path   LOW     t  HIGH     t
1 DC -> CA1 0.213 2.555 0.034 0.314
2   DC -> P 0.436 5.901 0.417 4.648
3  P -> CA1 0.187 2.206 0.276 2.776
> R
       Path   LOW     t  HIGH     t
1 DC -> CA1 0.269 2.815 0.069 0.646
2   DC -> R 0.112 1.004 0.338 3.957
3  R -> CA1 0.117 1.456 0.260 2.565
>

all items less controls

       Path   LOW     t  HIGH     t
1 DC -> CA1 0.355 4.786 0.133 1.348
2   DC -> P 0.386 5.003 0.436 4.739
3  P -> CA1 0.155 1.985 0.232 2.311
> R
       Path   LOW     t  HIGH     t
1 DC -> CA1 0.417 6.879 0.144 1.484
2   DC -> R 0.388 6.092 0.534 7.039
3  R -> CA1 0.017 0.214 0.211 2.030
